### 2023-03-07 outputs/paper/paper.qmd
initial commit

---
title: "GSS Education Analysis (Working Title)"
subtitle: "GSS Education Analysis (Working Subtitle)"
author: 
  - Emily Kim
  - Huda Sahaf
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "abstract (work in progress)"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false

#### Load Library ####
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(modelsummary)

#### Import cleaned_gss_2021.csv ####
cleaned_gss_2021 <-
  read.csv(here::here("./inputs/data/2021_data/cleaned_gss_2021.csv"))

```

```{r}
#| include: false

#### Ordering Highest Year of Education Achieved ####

cleaned_gss_2021$educ <- 
  factor(cleaned_gss_2021$educ, 
         levels = c("8th Grade", "9th Grade", "10th Grade", "11th Grade", "12th Grade", "1 Year of College", "2 Years of College", "3 Years of College", "4 Years of College", "5 Years of College", "6 Years of College", "7 Years of College", "8 Years of College"))

```

```{r}
#| echo: false
#| warning: false
#| label: fig-1
#| fig-cap: "Respondent's Sex by Highest Year of Education Achieved"

#### Creating Graph to Compare Sex Against Year of Completed Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = educ)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Highest Year Completed of Education")

```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$degree <- 
  factor(cleaned_gss_2021$degree, 
         levels = c("Less Than High School", "High School", "Associate / Junior College", "Bachelors Degree", "Graduate Degree"))

```

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "Respondent's Sex by Highest Level of Education"

#### Creating Graph to Compare Sex Against Level of Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Degree")+
  scale_fill_brewer(palette = "Pastel1")

```
```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Respondent's Sex by Highest Level of Education"

#### Creating Graph to Compare Sex Against Level of Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = richwork)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Rich Work")+
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$satjob <- 
  factor(cleaned_gss_2021$satjob, 
         levels = c("Very Satisfied", "Moderately Satisfied", "A Little Dissatisfied", "Very Dissatisfied"))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "Respondent's Sex by Job Satisfaction"

#### Creating Graph to Compare Sex Against Job Satisfaction ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$finrela <- 
  factor(cleaned_gss_2021$finrela, 
         levels = c("Far Above Average", "Above Average", "Average", "Below Average", "Far Below Average"))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-5
#| fig-cap: "Respondent's Sex by Self-Defined Financial Ranking Against Other US Families"

#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
#| echo: false
#| warning: false
#| label: fig-6
#| fig-cap: "Respondent's Highest Level of Education by Self-Defined Financial Ranking Against Other US Families"

#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.position = "bottom")
```

```{r}
#| echo: false
#| warning: false
#| label: fig-7
#| fig-cap: "Respondent's Highest Level of Education by Job Satisfaction"

#### Creating Graph to Compare Sex Against Job Satisfaction ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.position = "bottom")
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$class <- 
  factor(cleaned_gss_2021$class, 
         levels = c("Lower Class", "Working Class", "Middle Class", "Upper Class"))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-8
#| fig-cap: "Respondent's Highest Level of Education by Self-Ascribed Social Class"

#### Creating Graph to Compare Sex Against Self-Ascribed Social Class ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1")
```

# Introduction

# Data {#sec-data}

# Measurement

# Results

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {.unnumbered}

# Additional details

\newpage

# References

### 2023-03-07 scripts/00-simulate_data.R
initial commit

@@ -1,0 +1,121 @@
+#### Preamble ####
+# Purpose: Simulates relevant data from the 2021 US General Social Survey which can be downloaded from https://gss.norc.org/get-the-data/stata
+# Author: Chloe Thierstein, Huda Sahaf, Emily Kim 
+# Contact: chloe.thierstein@utoronto.ca, huda.sahaf@mail.utoronto.ca, emilyuna.kim@mail.utoronto.ca
+# Date: 6 March 2023 
+# License: MIT
+# Pre-requisites: To understand data need to know where to find the 2021 US General Social Survey data
+
+
+#### Need to Install These Packages to Run Script ####
+# install.packages("tibble")
+
+
+#### Workspace setup ####
+library(tibble)
+library()
+
+
+#### Simulate data ####
+
+set.seed(853)
+
+simulated_gss_2021 <-
+  tibble(
+    "highest_year_of_education" = sample(
+      x = c(
+        "7th Grade",
+        "8th Grade",
+        "9th Grade",
+        "10th Grade",
+        "11th Grade",
+        "12th Grade",
+        "1 Year of College",
+        "2 Years of College",
+        "3 Years of College",
+        "4 Years of College",
+        "5 Years of College",
+        "6 Years of College",
+        "7 Years of College",
+        "8 Years of College"
+      ),
+      size = 4032,
+      replace = TRUE
+    ),
+    "highest_level_of_education" = sample(
+      x = c(
+        "Less Than High School",
+        "High School",
+        "Associate / Junior College",
+        "Bachelors Degree",
+        "Graduate Degree"
+      ),
+      size = 4032,
+      replace = TRUE
+    ),
+    "respondents_sex" = sample(
+      x = c(
+        "Male",
+        "Female"
+      ),
+      size = 4032,
+      replace = TRUE
+    ),
+    "job_satisfaction" = sample(
+      x = c(
+        "Very Satisfied",
+        "Moderately Satisfied",
+        "A Little Dissatisfied",
+        "Very Dissatisfied"
+      ),
+      size = 4032,
+      replace = TRUE
+    ),
+    "impact_of_winning_money_on_maintaining_employment" = sample(
+      x = c(
+        "Continue to Work",
+        "Stop Working"
+      ),
+      size = 4032,
+      replace = TRUE
+    ),
+    "self_ascribed_social_class" = sample(
+      x = c(
+        "Lower Class",
+        "Working Class",
+        "Middle Class",
[…]

### 2023-03-07 scripts/01-download_data.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Read in data from GSS Link:https://gss.norc.org/get-the-data/stata
+# Author: Chloe Thierstein, Huda Sahaf, Emily Kim 
+# Contact: chloe.thierstein@utoronto.ca, huda.sahaf@mail.utoronto.ca, emilyuna.kim@mail.utoronto.ca
+# Date: 10 March 2023 
+# License: MIT
+# Prerequisites: Need to be able to access and download 2021 GSS data from https://gss.norc.org/get-the-data/stata
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace Set-up ####
+
+#### Installing Packages ####
+# install.packages("tidyverse") 
+# install.packages("haven") 
+# install.packages("here") 
+# install.packages("readr")
+# install.packages("dplyr")
+
+#### Opening Libraries ####
+
+library(tidyverse)
+library(haven)
+library(here)
+library(readr)
+library(dplyr)
+
+#### Read in Data ####
+
+#### Download data ####
+raw_gss_2021 <- read_dta("inputs/data/2021_stata/GSS2021.dta") # download .dta file from US GSS first and put "GSS2021.dta" folder into data folder 
+
+
+
+#### Save Data as CSV File ####
+write_csv(
+  x = raw_gss_2021, # name .csv file 
+  file = "raw_gss_2021.csv" # create raw data .csv file and store it in inputs folder
+)
+
+
+
+         

### 2023-03-07 scripts/02-data_cleaning.R

@@ -1,0 +1,162 @@
+#### Preamble ####
+# Purpose: Cleans data from the 2021 US General Social Survey downloaded from https://gss.norc.org/get-the-data/stata
+# Author: Chloe Thierstein, Huda Sahaf, Emily Kim 
+# Contact: chloe.thierstein@utoronto.ca, huda.sahaf@mail.utoronto.ca, emilyuna.kim@mail.utoronto.ca
+# Date: 10 March 2023 
+# License: MIT
+# Pre-requisites: Need to be able to access and download 2021 GSS data from https://gss.norc.org/get-the-data/stata
+# Any other information needed? Need to be able to access the 2021 GSS Codebook to understand how values were relabelled.
+
+#### Need to Install These Packages to Run Script ####
+# install.packages("dplyr")
+# install.packages("tidyverse")
+# install.packages("janitor")
+# install.packages("readr")
+# install.packages("haven")
+# install.packages("labelled")
+
+#### Workspace Setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(haven)
+library(here)
+library(labelled)
+
+#### Load Raw Data ####
+raw_gss_2021 <- read.csv(here::here("./inputs/data/2021_data/raw_gss_2021.csv"))
+
+#### Data Cleaning ####
+
+#### Clean Names ####
+cleaned_gss_2021 <- 
+  clean_names(raw_gss_2021)
+  
+#### Select Relevant Columns ####
+cleaned_gss_2021 <-
+  cleaned_gss_2021 |>
+  select(educ, degree, sex, satjob, richwork, class, satfin, finrela)
+
+#### Removing NA Rows from Data ####
+cleaned_gss_2021 <- 
+  cleaned_gss_2021|>
+  na.omit(datacollected) 
+
+#### Removing Label to be Able to Make Data More Meaningful ####
+unlabelled(cleaned_gss_2021)
+
+#### Re-coding Highest Year of School Completed to be More Meaningful ####
+cleaned_gss_2021 <- cleaned_gss_2021 |>
+  mutate(
+    educ = 
+      recode(
+        educ,
+        "8" = "8th Grade",
+        "9" = "9th Grade",
+        "10" = "10th Grade",
+        "11" = "11th Grade",
+        "12" = "12th Grade",
+        "13" = "1 Year of College",
+        "14" = "2 Years of College",
+        "15" = "3 Years of College",
+        "16" = "4 Years of College",
[…]

### 2023-03-07 scripts/04-test_data.R

@@ -1,0 +1,32 @@
+#### Preamble ####
+# Purpose: Tests simulated data of the 2021 Us General Social Survey. The real data can be downloaded from https://gss.norc.org/get-the-data/stata
+# Author: Chloe Thierstein, Huda Sahaf, Emily Kim 
+# Contact: chloe.thierstein@utoronto.ca, huda.sahaf@mail.utoronto.ca, emilyuna.kim@mail.utoronto.ca
+# Date: 6 March 2023 
+# License: MIT
+# Pre-requisites: Need to be able to load in simulated data
+
+#### Need to Install These Packages to Run Script ####
+# install.packages("here")
+
+#### Workspace setup ####
+library(here)
+
+#### Load in Simulated Data ####
+simulated_gss_2021 <- read.csv(here::here("./inputs/data/2021_simulated_data/simulated_gss_2021.csv"))
+
+#### Testing Simulated Data ####
+
+#### Test 1 ####
+simulated_gss_2021$"highest_year_of_education" |>
+  unique()|>
+  length() == 14
+
+#### Test 2 ####
+simulated_gss_2021$"respondents_sex" |>
+  class() == "character"
+
+#### Test 3 ####
+simulated_gss_2021$"financial_satisfaction" |>
+  unique()
+

### 2023-03-07 outputs/paper/paper.qmd
update legends

@@
   - Chloe Thierstein
-thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git."
+thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git"
 date: "`r Sys.time()`"
@@
        y = "Number",
-       fill = "Highest Year Completed of Education")
+       fill = "Highest Year of Education Completed")+
+  theme(legend.key.size = unit(1,"line"))
 
@@
 ```
+
 ```{r}
@@
   scale_fill_brewer(palette = "Pastel1")+
-  theme(legend.position = "bottom")
+  theme(legend.title = element_text(size = 6),
+        legend.text= element_text(size=6))
 ```
@@
        fill = "Self-Ascribed Class")+
-  scale_fill_brewer(palette = "Pastel1")
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
 ```

### 2023-03-12 outputs/paper/paper.qmd
add graphs

@@
 ```
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-9
+#| fig-cap: "rich work vs class"
+
+#### Creating Graph ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(x = richwork, fill = class)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(x = "richwork",
+       y = "number",
+       fill = "class")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-10
+#| fig-cap: "richwork vs satfin"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(x = richwork, fill = satfin)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(x = "richwork",
+       y = "number",
+       fill = "satfin")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-11
+#| fig-cap: "richwork vs finrela"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(x = richwork, fill = finrela)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(x = "richwork",
+       y = "number",
+       fill = "finrela")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-12
+#| fig-cap: "satfin vs satjob"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = satfin, fill = satjob)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "satfin",
+       x = "number",
+       fill = "satjob")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-13
+#| fig-cap: "satfin vs class"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = satfin, fill = class)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "satfin",
+       x = "number",
+       fill = "class")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-14
+#| fig-cap: "satfin vs finrela"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = satfin, fill = finrela)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "satfin",
+       x = "number",
+       fill = "finrela")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-15
+#| fig-cap: "satfin vs degree"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = satfin, fill = degree)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "satfin",
+       x = "number",
+       fill = "degree")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-16
+#| fig-cap: "finrela vs class"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = finrela, fill = class)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "finrela",
+       x = "number",
+       fill = "class")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-17
+#| fig-cap: "finrela vs satjob"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = finrela, fill = satjob)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "finrela",
+       x = "number",
+       fill = "satjob")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-18
+#| fig-cap: "finrela vs satjob"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = finrela, fill = satfin)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "finrela",
+       x = "number",
+       fill = "satfin")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
 

### 2023-03-12 outputs/paper/paper.qmd
update graphs

@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-19
+#| fig-cap: "degree"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = degree, fill = degree)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "degree",
+       x = "number")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
 # Introduction

### 2023-03-12 outputs/paper/paper.qmd
add graphs

@@
 
+```{r}
+
+#| echo: false
+#| warning: false
+#| label: fig-20
+#| fig-cap: "degree"
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = happy, fill = degree)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "happy",
+       x = "number")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
 # Introduction

### 2023-03-12 scripts/02-data_cleaning.R

@@ -35,7 +35,7 @@ cleaned_gss_2021 <-
 #### Select Relevant Columns ####
 cleaned_gss_2021 <-
   cleaned_gss_2021 |>
-  select(educ, degree, sex, satjob, richwork, class, satfin, finrela)
+  select(happy, educ, degree, sex, satjob, richwork, class, satfin, finrela)
 
 #### Removing NA Rows from Data ####
 cleaned_gss_2021 <- 
@@ -44,6 +44,18 @@ cleaned_gss_2021 <-
 
 #### Removing Label to be Able to Make Data More Meaningful ####
 unlabelled(cleaned_gss_2021)
+
+#### Re-coding How Respondent's Describe Their Financial Ranking against Other Americans to be More Meaningful ####
+cleaned_gss_2021 <- cleaned_gss_2021 |>
+  mutate(
+    happy =
+      recode(
+        happy,
+        "1" = "Very Happy",
+        "2" = "Pretty Happy",
+        "3" = "Not Too Happy"
+      )
+  )
 
 #### Re-coding Highest Year of School Completed to be More Meaningful ####
 cleaned_gss_2021 <- cleaned_gss_2021 |>

### 2023-03-14 outputs/paper/paper.qmd
fix graphs
add variables table

--- 2023-03-12 outputs/paper/paper.qmd
@@
 library(modelsummary)
+library(kableExtra)
+library(knitr)
 
@@
 
-#### Ordering Highest Year of Education Achieved ####
+#### Create Variable Description Tibble ####
 
-cleaned_gss_2021$educ <- 
-  factor(cleaned_gss_2021$educ, 
-         levels = c("8th Grade", "9th Grade", "10th Grade", "11th Grade", "12th Grade", "1 Year of College", "2 Years of College", "3 Years of College", "4 Years of College", "5 Years of College", "6 Years of College", "7 Years of College", "8 Years of College"))
-
+ variable_table <-
+  tibble(
+    "Variable" = c(
+      "class",
+      "degree",
+      "finrela",
+      "happy",
+      "satjob",
+      "satfin",
+      "sex"
+    ),
+    "Variable Description" = c(
+      "Self-ascribed class of the respondent",
+      "Highest level of education achieved by respondent",
+      "Self-ascribed ranking of respondnet when compared to other US households",
+      "Respondent's rating of how happy they are daily",
+      "Level of satisfaction with the work respondents do",
+      "Level of satisfaction with the job respondents have",
+      "Sex of the respondent"
+    )
+  )
 ```
@@
 #| warning: false
-#| label: fig-1
-#| fig-cap: "Respondent's Sex by Highest Year of Education Achieved"
+#| label: tbl-1
+#| tbl-cap: "Variable Descriptions"
 
-#### Creating Graph to Compare Sex Against Year of Completed Education ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = educ)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number",
-       fill = "Highest Year of Education Completed")+
-  theme(legend.key.size = unit(1,"line"))
+#### Add Variable Table ####
+variable_table |>
+  kable(booktabs = TRUE) |>
+  kable_styling(font_size = 7, latex_options = "hold_position")
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-20
+#| fig-cap: "happy vs degree"
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = degree, fill = happy)) +
+  geom_bar() +
+  theme_classic() +
+  labs(y = "degree",
+       x = "number")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
 # Introduction

### 2023-03-14 scripts/02-data_cleaning.R
add happy variable and remove educ variable

@@ -35,7 +35,7 @@ cleaned_gss_2021 <-
 #### Select Relevant Columns ####
 cleaned_gss_2021 <-
   cleaned_gss_2021 |>
-  select(happy, educ, degree, sex, satjob, richwork, class, satfin, finrela)
+  select(happy, degree, sex, satjob, richwork, class, satfin, finrela)
 
 #### Removing NA Rows from Data ####
 cleaned_gss_2021 <- 
@@ -57,27 +57,7 @@ cleaned_gss_2021 <- cleaned_gss_2021 |>
       )
   )
 
-#### Re-coding Highest Year of School Completed to be More Meaningful ####
-cleaned_gss_2021 <- cleaned_gss_2021 |>
-  mutate(
-    educ = 
-      recode(
-        educ,
-        "8" = "8th Grade",
-        "9" = "9th Grade",
-        "10" = "10th Grade",
-        "11" = "11th Grade",
-        "12" = "12th Grade",
-        "13" = "1 Year of College",
-        "14" = "2 Years of College",
-        "15" = "3 Years of College",
-        "16" = "4 Years of College",
-        "17" = "5 Years of College",
-        "18" = "6 Years of College",
-        "19" = "7 Years of College",
-        "20" = "8 Years of College"
-        )
-  )
+
 
 #### Re-coding Respondent's Highest Degree of Education to be More Meaningful ####
 cleaned_gss_2021 <- cleaned_gss_2021 |>
@@ -153,6 +133,9 @@ cleaned_gss_2021 <- cleaned_gss_2021 |>
       )
   )
 
+
+
+
 #### Re-coding How Respondent's Describe Their Financial Ranking against Other Americans to be More Meaningful ####
 cleaned_gss_2021 <- cleaned_gss_2021 |>
   mutate(
@@ -172,3 +155,5 @@ write_csv(
   x = cleaned_gss_2021,
   file = "cleaned_gss_2021.csv"
 ) #move this .csv to 2021_data folder
+
+

### 2023-03-14 outputs/paper/paper.qmd
add table of contents and label some sections

@@
 format: pdf
-number-sections: true
+toc: TRUE
+number-sections: TRUE
 bibliography: references.bib
@@
 
-# Introduction
+# Introduction {#sec-introduction}
 
@@
 
+## Data Management {#sec-first-point}
+
+## Source and Methodology
+
+## Sampling
+
+## Weighting
+
+## Key Features
+
 # Measurement
 
-# Results
+# Results {#sec-results}
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-# Appendix {.unnumbered}
-
-# Additional details
+# Appendix
 

### 2023-03-14 outputs/paper/paper.qmd
reorganize paper

@@
 ```
+
+# Introduction {#sec-introduction}
+
+# Data {#sec-data}
+
+## Data Management {#sec-first-point}
+
+This paper utilzes the R statistical programming language \[citer\], along with several packages, tidyverse \[citetidyverse\], here \[citehere\], janitor \[citejanitor\],and dplyr \[citedplyr\].
+All figures in this paper have been created using the packages ggplot2 \[citeggplot\] and the tables have been created using knitr \[citeknitr\] and kableExtra \[citekableextra\].
+The color styles in graphs have been created using the RColorBrewer packages \[citercolorbrewer\] and all graph combinations were created using the patchwork package \[citepatchwork\].
+
+## Source and Methodology
+
+All data within this paper are extracted from the 2021 United States General Social Survey (GSS).
+This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends \[citegsscodebook\].
+Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires \[citegsscodebook\].
+The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures \[citegsscodebook\].
+
+## Sampling
+
+The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing \[citegsscodebook\].
+This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses \[citegsscodebook\].
+From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch \[citegsscodebook\].
+Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 surveys released \[citegsscodebook\].
+
+## Weighting
+
+## Key Features
 
@@
 ```
+
+# Measurement
+
+# Results {#sec-results}
+
+# Discussion
+
+## The American Dream
+
+The United States is built upon individualism, which trickles into their definitions of financial security, happiness, and overall fulfillment and satisfaction in life.
+Wellbeing of individuals within the United States therefore, is tracked and monitored through a variety of different factors.
+The aim of this investigation was to determine whether higher educational achievement influenced an individuals perceptions of social class, degree of financial satisfaction and job satisfaction.
+These factors were chosen because of their significance with regards to the American Dream, a concept that is built off a linear pattern of behavior in terms of economic security.
+Hustle culture is popular within the United States as an extension of the American Dream, because the idea that an individual must work hard in order to reap the benefits in terms is what drives culture within America.
+
+According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement(citation).
+These are the fundamentals in terms of how Americans generally define their wellbeing in society.
+However, no matter how linear an American\'s personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
+But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.
+
+The assumption in general is a higher degree of education translates so an overall greater quality of life or well-being, greater job satisfaction, higher social class, etc.
+However, we found that this was not necessarily the case.
+Overall out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor\'s degree.
+The level of education was compared to a few variables: overall happiness, self-ascribed social class, job satisfaction, and financial ranking against other families in the US.
+
+## Social Class
+
+Researchers have investigated the correlation between education and happiness, with several studies indicating that a higher level of education is positively associated with greater levels of happiness.
+This relationship may be explained by the fact that education can impact one\'s self-ascribed social class, which in turn can influence their notion of happiness.
+Higher education can provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility, leading to a higher sense of social status.
+As a result, these individuals may experience greater life satisfaction, which contributes to their overall sense of happiness and security.
+
+In a 2020 article published in the Journal of Personality and Social Psychology, authors Siyu Yu and Steven L.
+Blader examined the impact of status and social class on subjective well-being (SWB).
+They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB **\[cite page 333\]**.
+Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
+As shown in **Figure 15**, we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting \"Pretty Well Satisfied\" and \"More or Less Satisfied\" than those selecting \"Not Satisfied at All\".
+Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.
+
+Overall, there seems to be a significant relationship between education, social class, and one\'s perceived well-being.
+Education can serve as a key factor in determining an individual\'s social class as it unlocks opportunities for resources and mobility, which in turn can impact their sense of status and overall sense of happiness.
+At the same time, while higher levels of education may be generally associated with greater levels of happiness, this relationship may not always be a cause and effect correlation.
+Subjective well-being may be further influenced by other factors such as personal values, cultural background, and social support.
+It is important to consider these important nuances when examining the data in order to develop a more comprehensive understanding of how variables interact and impact individuals\' lives.
+This will be further explored in the weaknesses, ethics, and bias section of this paper.
+
+## Second discussion point
+
+## Third discussion point
+
+## Weaknesses and next steps
+
+There are several limitations to this paper.
+One weakness is that our insights rely on data from the General Social Survey (GSS), which is a cross-sectional survey that collects data at a single point in time.
+While it can be useful for exploring relationships between variables and generating hypotheses, it cannot establish causality between variables, has limited ability to assess change over time, and has potential for selection bias if participants are not representative of the population of interest **\[cite article\]**.
+Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one\'s overall well-being.
+GSS responses are subject to influence by external factors such as recall bias, in which participants may have left out details when reporting about their subjective experiences.
+
+Another potential ethical concern is that our paper may perpetuate the notion that higher education is the only solution to achieving happiness and success, disregarding the presence of systemic inequalities such as racism and economic inequality that can limit access to education and social mobility.
+Moreover, the sample survey in the GSS may not fully represent the experiences of more marginalized groups, which point to the need for further research and survey strategies that incorporate more diverse perspectives.
+
+In sum, while the paper provides valuable insights on the relationship between education and self-perceived happiness, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our findings.
 
@@
 
-# Introduction {#sec-introduction}
-
-# Data {#sec-data}
-
-## Data Management {#sec-first-point}
-
-## Source and Methodology
-
-## Sampling
-
-## Weighting
-
-## Key Features
-
-# Measurement
-
-# Results {#sec-results}
-
-# Discussion
-
-## First discussion point
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
+\
 

### 2023-03-14 outputs/paper/paper.qmd
reorganize paper

@@
 thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git"
-date: "`r Sys.time()`"
+date: "March 16, 2023"
 date-format: "D MMMM YYYY"
@@
 
-This paper utilzes the R statistical programming language \[citer\], along with several packages, tidyverse \[citetidyverse\], here \[citehere\], janitor \[citejanitor\],and dplyr \[citedplyr\].
-All figures in this paper have been created using the packages ggplot2 \[citeggplot\] and the tables have been created using knitr \[citeknitr\] and kableExtra \[citekableextra\].
-The color styles in graphs have been created using the RColorBrewer packages \[citercolorbrewer\] and all graph combinations were created using the patchwork package \[citepatchwork\].
+This paper utilzes the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidyverse], here [@citehere], janitor [@citejanitor],and dplyr [@citedplyr].
+All figures in this paper have been created using the packages ggplot2 [@citeggplot2] and the tables have been created using knitr [@citeknitr] and kableExtra [@citekablextra].
+The color styles in graphs have been created using the RColorBrewer packages [@citercolorbrewer].
 
@@
 All data within this paper are extracted from the 2021 United States General Social Survey (GSS).
-This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends \[citegsscodebook\].
-Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires \[citegsscodebook\].
-The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures \[citegsscodebook\].
+This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends **\[citegsscodebook\].** Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires **\[citegsscodebook\]**.
+The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures **\[citegsscodebook\].**
 
@@
 
-The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing \[citegsscodebook\].
-This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses \[citegsscodebook\].
-From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch \[citegsscodebook\].
-Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 surveys released \[citegsscodebook\].
+The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing **\[citegsscodebook\].** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses **\[citegsscodebook\]**.
+From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 surveys released **\[citegsscodebook\].**
 
@@
 
-## Weaknesses and next steps
+## Limitations and weaknesses
 

### 2023-03-14 outputs/paper/paper.qmd
update paper sections

@@
 library(knitr)
+library(dplyr)
 
@@
 These are the fundamentals in terms of how Americans generally define their wellbeing in society.
-However, no matter how linear an American\'s personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
+However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
 But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.
@@
 However, we found that this was not necessarily the case.
-Overall out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor\'s degree.
+Overall out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor's degree.
 The level of education was compared to a few variables: overall happiness, self-ascribed social class, job satisfaction, and financial ranking against other families in the US.
@@
 Researchers have investigated the correlation between education and happiness, with several studies indicating that a higher level of education is positively associated with greater levels of happiness.
-This relationship may be explained by the fact that education can impact one\'s self-ascribed social class, which in turn can influence their notion of happiness.
+This relationship may be explained by the fact that education can impact one's self-ascribed social class, which in turn can influence their notion of happiness.
 Higher education can provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility, leading to a higher sense of social status.
@@
 Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-As shown in **Figure 15**, we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting \"Pretty Well Satisfied\" and \"More or Less Satisfied\" than those selecting \"Not Satisfied at All\".
+As shown in **Figure 15**, we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
 Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.
 
-Overall, there seems to be a significant relationship between education, social class, and one\'s perceived well-being.
-Education can serve as a key factor in determining an individual\'s social class as it unlocks opportunities for resources and mobility, which in turn can impact their sense of status and overall sense of happiness.
+Overall, there seems to be a significant relationship between education, social class, and one's perceived well-being.
+Education can serve as a key factor in determining an individual's social class as it unlocks opportunities for resources and mobility, which in turn can impact their sense of status and overall sense of happiness.
 At the same time, while higher levels of education may be generally associated with greater levels of happiness, this relationship may not always be a cause and effect correlation.
 Subjective well-being may be further influenced by other factors such as personal values, cultural background, and social support.
-It is important to consider these important nuances when examining the data in order to develop a more comprehensive understanding of how variables interact and impact individuals\' lives.
+It is important to consider these important nuances when examining the data in order to develop a more comprehensive understanding of how variables interact and impact individuals' lives.
 This will be further explored in the weaknesses, ethics, and bias section of this paper.
-
-## Second discussion point
 
@@
 While it can be useful for exploring relationships between variables and generating hypotheses, it cannot establish causality between variables, has limited ability to assess change over time, and has potential for selection bias if participants are not representative of the population of interest **\[cite article\]**.
-Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one\'s overall well-being.
+Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one's overall well-being.
 GSS responses are subject to influence by external factors such as recall bias, in which participants may have left out details when reporting about their subjective experiences.

### 2023-03-15 outputs/paper/paper.qmd
remove unnecessary graphs

@@
 
-## Source and Methodology
+## Source
 
@@
 The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing **\[citegsscodebook\].** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses **\[citegsscodebook\]**.
-From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 surveys released **\[citegsscodebook\].**
+From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 total surveys released **\[citegsscodebook\].**
 
-## Weighting
+## Methodology
+
+As mentioned previously, this paper utilizes data from the 2021 US General Social Survey (GSS).
 
 ## Key Features
+
+This paper is assessing our estimand 1,567 responses of the 3,731 complete responses received which represents 42% of the complete respondents and only 5.7% of the total surveys released.
+Respondent's to the 2021 GSS are males or female US citizens, not living in institutional housing, who are over the age of 18 **\[citegsscodebook\]**.
+In our analysis we removed 2,164 responses to account for unanswered or not applicable responses.
+We did this to ensure that the data used in this paper is complete and representative of all variables.
+The variables we selected for our analysis and their measurement levels can be seen in @tbl-1.
 
@@
 
-# Measurement
+# Results {#sec-results}
 
-# Results {#sec-results}
+```{r}
+#| include: false
+
+#### Ordering ####
+
+cleaned_gss_2021$satjob <- 
+  factor(cleaned_gss_2021$satjob, 
+         levels = c("Very Satisfied", "Moderately Satisfied", "A Little Dissatisfied", "Very Dissatisfied"))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-4
+#| fig-cap: "Respondent's Sex by Job Satisfaction"
+
+#### Creating Graph to Compare Sex Against Job Satisfaction ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(x = sex, fill = satjob)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(x = "Sex",
+       y = "Number",
+       fill = "Job Satisfaction")+
+  scale_fill_brewer(palette = "Pastel1")
+```
 
@@
 The United States is built upon individualism, which trickles into their definitions of financial security, happiness, and overall fulfillment and satisfaction in life.
-Wellbeing of individuals within the United States therefore, is tracked and monitored through a variety of different factors.
+Well-being of individuals within the United States therefore, is tracked and monitored through a variety of different factors.
 The aim of this investigation was to determine whether higher educational achievement influenced an individuals perceptions of social class, degree of financial satisfaction and job satisfaction.
@@
 
-According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement(citation).
-These are the fundamentals in terms of how Americans generally define their wellbeing in society.
+According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement**(citation).** These are the fundamentals in terms of how Americans generally define their well-being in society.
 However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
@@
 In sum, while the paper provides valuable insights on the relationship between education and self-perceived happiness, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our findings.
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-2
-#| fig-cap: "Respondent's Sex by Highest Level of Education"
-
-#### Creating Graph to Compare Sex Against Level of Education ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = degree)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number",
-       fill = "Degree")+
-  scale_fill_brewer(palette = "Pastel1")
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-3
-#| fig-cap: "Respondent's Sex by Highest Level of Education"
-
-#### Creating Graph to Compare Sex Against Level of Education ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = richwork)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number",
-       fill = "Rich Work")+
-  scale_fill_brewer(palette = "Pastel1")
-```
-
-```{r}
-#| include: false
-
-#### Ordering ####
-
-cleaned_gss_2021$satjob <- 
-  factor(cleaned_gss_2021$satjob, 
-         levels = c("Very Satisfied", "Moderately Satisfied", "A Little Dissatisfied", "Very Dissatisfied"))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-4
-#| fig-cap: "Respondent's Sex by Job Satisfaction"
-
-#### Creating Graph to Compare Sex Against Job Satisfaction ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number",
-       fill = "Job Satisfaction")+
-  scale_fill_brewer(palette = "Pastel1")
-```
 
@@
 #| warning: false
-#| label: fig-8
-#| fig-cap: "Respondent's Highest Level of Education by Self-Ascribed Social Class"
-
-#### Creating Graph to Compare Sex Against Self-Ascribed Social Class ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = class)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "Highest Level of Education",
-       x = "Number",
-       fill = "Self-Ascribed Class")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-9
-#| fig-cap: "rich work vs class"
-
-#### Creating Graph ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = richwork, fill = class)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "richwork",
-       y = "number",
-       fill = "class")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-10
-#| fig-cap: "richwork vs satfin"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = richwork, fill = satfin)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "richwork",
-       y = "number",
-       fill = "satfin")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-11
-#| fig-cap: "richwork vs finrela"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = richwork, fill = finrela)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "richwork",
-       y = "number",
-       fill = "finrela")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-12
-#| fig-cap: "satfin vs satjob"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = satfin, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "satfin",
-       x = "number",
-       fill = "satjob")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-13
-#| fig-cap: "satfin vs class"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = satfin, fill = class)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "satfin",
-       x = "number",
-       fill = "class")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-14
-#| fig-cap: "satfin vs finrela"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = satfin, fill = finrela)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "satfin",
-       x = "number",
-       fill = "finrela")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
 #| label: fig-15
@@
        fill = "degree")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-16
-#| fig-cap: "finrela vs class"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = class)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "finrela",
-       x = "number",
-       fill = "class")+
   scale_fill_brewer(palette = "Pastel1") +
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-19
-#| fig-cap: "degree"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = degree)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "degree",
-       x = "number")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-20
-#| fig-cap: "happy vs degree"
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = happy)) +
-  geom_bar() +
-  theme_classic() +
-  labs(y = "degree",
-       x = "number")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
 \

### 2023-03-15 outputs/paper/paper.qmd
reorder paper and relabel graphs

@@
 
-```{r}
-#| include: false
-
-#### Ordering ####
-
-cleaned_gss_2021$degree <- 
-  factor(cleaned_gss_2021$degree, 
-         levels = c("Less Than High School", "High School", "Associate / Junior College", "Bachelors Degree", "Graduate Degree"))
-
-```
-
 # Results {#sec-results}
@@
 
-#### Ordering ####
+#### Ordering Highest-Level of Education to be Easier to Read in Graphs####
+
+cleaned_gss_2021$degree <- 
+  factor(cleaned_gss_2021$degree, 
+         levels = c("Less Than High School", "High School", "Associate / Junior College", "Bachelors Degree", "Graduate Degree"))
+```
+
+```{r}
+#| include: false
+
+#### Ordering Job Satisfaction to be Easier to Read in Graphs####
 
@@
 ```{r}
+#| include: false
+
+#### Ordering Self-Ascribed Financial Wellness Compared to Other US Families ####
+
+cleaned_gss_2021$finrela <- 
+  factor(cleaned_gss_2021$finrela, 
+         levels = c("Far Above Average", "Above Average", "Average", "Below Average", "Far Below Average"))
+```
+
+```{r}
+#| include: false
+
+#### Ordering Self-Ascribed Social Class of Respondents####
+
+cleaned_gss_2021$class <- 
+  factor(cleaned_gss_2021$class, 
+         levels = c("Lower Class", "Working Class", "Middle Class", "Upper Class"))
+```
+
+```{r}
 #| echo: false
 #| warning: false
-#| label: fig-4
-#| fig-cap: "Respondent's Sex by Job Satisfaction"
+#| label: fig-5
+#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex"
 
-#### Creating Graph to Compare Sex Against Job Satisfaction ####
+#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex ####
 
 cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = satjob)) +
+  ggplot(mapping = aes(x = sex, fill = finrela)) +
   geom_bar() + 
@@
   labs(x = "Sex",
-       y = "Number",
+       y = "Number of Respondents",
+       fill = "Rating Against Other US Families")+
+  scale_fill_brewer(palette = "Pastel1")
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-6
+#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Highest Level of Education Achieved"
+
+#### Creating Graph to Compare Respondent's Self-Asscribed FinancialRanking Against Other US Families by Their Highest Level of Education Achieved ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = degree, fill = finrela)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "Highest Level of Education Achieved",
+       x = "Number of Respondents",
+       fill = "Rating Against Other US Families")+
+  scale_fill_brewer(palette = "Pastel1")+
+  theme(legend.title = element_text(size = 6),
+        legend.text= element_text(size=6))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-7
+#| fig-cap: "Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved"
+
+#### Creating Graph to Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = degree, fill = satjob)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "Highest Level of Education Achieved",
+       x = "Number of Respondents",
        fill = "Job Satisfaction")+
-  scale_fill_brewer(palette = "Pastel1")
+  scale_fill_brewer(palette = "Pastel1")+
+  theme(legend.title = element_text(size = 6),
+        legend.text= element_text(size=6))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-15
+#| fig-cap: "Respondent's Report of Financial Satisfaction by Their Highest Level of Education Achieved"
+
+#### Creating Graph to Compare Respondent's Report of Financial Satisfaction by Their Highest Level of Education Achieved ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = satfin, fill = degree)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "Financial Satisfaction",
+       x = "Number of Respondents",
+       fill = "Highest Level of Education Achieved")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-17
+#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families"
+
+#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = finrela, fill = satjob)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "Rating Against Other US Families",
+       x = "Number of Respondents",
+       fill = "Job Satisfaction")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-18
+#| fig-cap: "finrela vs satjob"
+
+#### Creating Graph to  ####
+
+cleaned_gss_2021 |>
+  ggplot(mapping = aes(y = finrela, fill = satfin)) +
+  geom_bar() + 
+  theme_classic() +
+  labs(y = "Rating Against Other US Families",
+       x = "Number of Respondents",
+       fill = "Financial Satisfaction")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
 ```
@@
 
-```{r}
-#| include: false
-
-#### Ordering ####
-
-cleaned_gss_2021$finrela <- 
-  factor(cleaned_gss_2021$finrela, 
-         levels = c("Far Above Average", "Above Average", "Average", "Below Average", "Far Below Average"))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-5
-#| fig-cap: "Respondent's Sex by Self-Defined Financial Ranking Against Other US Families"
-
-#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = finrela)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number",
-       fill = "Rating Against Other Families")+
-  scale_fill_brewer(palette = "Pastel1")
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-6
-#| fig-cap: "Respondent's Highest Level of Education by Self-Defined Financial Ranking Against Other US Families"
-
-#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = finrela)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "Highest Level of Education",
-       x = "Number",
-       fill = "Rating Against Other Families")+
-  scale_fill_brewer(palette = "Pastel1")+
-  theme(legend.title = element_text(size = 6),
-        legend.text= element_text(size=6))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-7
-#| fig-cap: "Respondent's Highest Level of Education by Job Satisfaction"
-
-#### Creating Graph to Compare Sex Against Job Satisfaction ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "Highest Level of Education",
-       x = "Number",
-       fill = "Job Satisfaction")+
-  scale_fill_brewer(palette = "Pastel1")+
-  theme(legend.title = element_text(size = 6),
-        legend.text= element_text(size=6))
-```
-
-```{r}
-#| include: false
-
-#### Ordering ####
-
-cleaned_gss_2021$class <- 
-  factor(cleaned_gss_2021$class, 
-         levels = c("Lower Class", "Working Class", "Middle Class", "Upper Class"))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-15
-#| fig-cap: "satfin vs degree"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = satfin, fill = degree)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "satfin",
-       x = "number",
-       fill = "degree")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-17
-#| fig-cap: "finrela vs satjob"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "finrela",
-       x = "number",
-       fill = "satjob")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-18
-#| fig-cap: "finrela vs satjob"
-
-#### Creating Graph to  ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = satfin)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "finrela",
-       x = "number",
-       fill = "satfin")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
 \

### 2023-03-15 outputs/paper/paper.qmd
add variable measurement table

@@
       "finrela",
-      "happy",
       "satjob",
@@
       "Self-ascribed ranking of respondnet when compared to other US households",
-      "Respondent's rating of how happy they are daily",
       "Level of satisfaction with the work respondents do",
@@
       "Sex of the respondent"
+    )
+  )
+```
+
+```{r}
+#| include: false
+
+#### Create Variable Description Tibble ####
+
+ variable_measure_table <-
+  tibble(
+    "Variable" = c(
+      "class",
+      "degree",
+      "finrela",
+      "satjob",
+      "satfin",
+      "sex"
+    ),
+    "Variable Measurement" = c(
+      "Lower Class, Working Class, Middle Class, Upper Class",
+      "Less Than High School, High School, Associate / Junior College, Bachelors, Graduate",
+      "Far Below Average, Below Average, Average, Above Average, Far Above Average",
+      "Very Satisfied, Moderately Satisfied, A Little Dissatisfied, Very Dissatisfied",
+      "Pretty Well Satisfied, More or Less Satisfied, Not Satisfied at All",
+      "Male, Female"
     )
@@
   kable(booktabs = TRUE) |>
-  kable_styling(font_size = 7, latex_options = "hold_position")
+  kable_styling(font_size = 9, latex_options = "hold_position")
 
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: tbl-2
+#| tbl-cap: "Variable Measurements"
+
+#### Add Variable Table ####
+variable_measure_table |>
+  kable(booktabs = TRUE) |>
+  kable_styling(font_size = 9, latex_options = "hold_position")
 ```

### 2023-03-15 scripts/02-data_cleaning.R
remove unncessary variables

@@ -5,7 +5,7 @@
 # Date: 10 March 2023 
 # License: MIT
 # Pre-requisites: Need to be able to access and download 2021 GSS data from https://gss.norc.org/get-the-data/stata
-# Any other information needed? Need to be able to access the 2021 GSS Codebook to understand how values were relabelled.
+# Any other information needed? Need to be able to access the 2021 GSS Codebook to understand how values were re-labelled.
 
 #### Need to Install These Packages to Run Script ####
 # install.packages("dplyr")
@@ -35,7 +35,7 @@ cleaned_gss_2021 <-
 #### Select Relevant Columns ####
 cleaned_gss_2021 <-
   cleaned_gss_2021 |>
-  select(happy, degree, sex, satjob, richwork, class, satfin, finrela)
+  select( degree, satjob, class, satfin, finrela)
 
 #### Removing NA Rows from Data ####
 cleaned_gss_2021 <- 
@@ -44,19 +44,6 @@ cleaned_gss_2021 <-
 
 #### Removing Label to be Able to Make Data More Meaningful ####
 unlabelled(cleaned_gss_2021)
-
-#### Re-coding How Respondent's Describe Their Financial Ranking against Other Americans to be More Meaningful ####
-cleaned_gss_2021 <- cleaned_gss_2021 |>
-  mutate(
-    happy =
-      recode(
-        happy,
-        "1" = "Very Happy",
-        "2" = "Pretty Happy",
-        "3" = "Not Too Happy"
-      )
-  )
-
 
 
 #### Re-coding Respondent's Highest Degree of Education to be More Meaningful ####
@@ -73,16 +60,6 @@ cleaned_gss_2021 <- cleaned_gss_2021 |>
       )
       )
 
-#### Re-coding Respondent's Sex to be More Meaningful ####
-cleaned_gss_2021 <- cleaned_gss_2021 |>
-  mutate(
-    sex = 
-      recode(
-        sex,
-        "1" = "Male",
-        "2" = "Female"
-      )
-  )
 
 #### Re-coding Respondent's Job Satisfaction to be More Meaningful ####
 cleaned_gss_2021 <- cleaned_gss_2021 |>
@@ -97,16 +74,7 @@ cleaned_gss_2021 <- cleaned_gss_2021 |>
       )
   )
 
-#### Re-coding Respondent's Willingness to Stop Working if They Become Rich to be More Meaningful ####
[…]

### 2023-03-15 outputs/paper/paper.qmd
update paper

@@
 
-# Data {#sec-data}
+# Data and methods {#sec-data}
 
@@
 
-## Methodology
-
-As mentioned previously, this paper utilizes data from the 2021 US General Social Survey (GSS).
-
 ## Key Features
 
-This paper is assessing our estimand 1,567 responses of the 3,731 complete responses received which represents 42% of the complete respondents and only 5.7% of the total surveys released.
+This paper is assessing our estimand of 1,567 responses of the 3,731 complete responses received which represents 42% of the complete respondents and only 5.7% of the total surveys released.
 Respondent's to the 2021 GSS are males or female US citizens, not living in institutional housing, who are over the age of 18 **\[citegsscodebook\]**.
@@
 We did this to ensure that the data used in this paper is complete and representative of all variables.
-The variables we selected for our analysis and their measurement levels can be seen in @tbl-1.
+The variables we selected for our analysis can be seen in @tbl-1 and their measurement levels can be seen in @tbl-2.
 
@@
       "satjob",
-      "satfin",
-      "sex"
+      "satfin"
     ),
@@
       "Level of satisfaction with the work respondents do",
-      "Level of satisfaction with the job respondents have",
-      "Sex of the respondent"
+      "Level of satisfaction with the job respondents have"
     )
@@
       "Very Satisfied, Moderately Satisfied, A Little Dissatisfied, Very Dissatisfied",
-      "Pretty Well Satisfied, More or Less Satisfied, Not Satisfied at All",
-      "Male, Female"
+      "Pretty Well Satisfied, More or Less Satisfied, Not Satisfied at All"
     )
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-5
-#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex"
-
-#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(x = sex, fill = finrela)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(x = "Sex",
-       y = "Number of Respondents",
-       fill = "Rating Against Other US Families")+
-  scale_fill_brewer(palette = "Pastel1")
-```
+When looking at @fig-1, we can see that the majority of respondents have only completed their high school diploma with the next highest response category being bachelor's degree and the third being graduate degrees.
+Generally respondents who identified as having their bachelor's degree or graduate degree reported being more likely to be "above average" and "far above average" than respondents who reported having an associate or junior college degree or lower.
+Interestingly, a large portion of respondents with higher levels of education still reported themselves as "average" when comparing themselves to other US families.
+Additionally, the rate at which those with less than a high school diploma and high school diplomas self-report ranking when compared to other US households decreases substantially at every measuring point as ranking increases.
 
@@
 #| warning: false
-#| label: fig-6
-#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Highest Level of Education Achieved"
+#| label: fig-1
+#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Highest Level of Education Achieved"
 
-#### Creating Graph to Compare Respondent's Self-Asscribed FinancialRanking Against Other US Families by Their Highest Level of Education Achieved ####
+#### Creating Graph to Compare Respondent's Self-Ascribed FinancialRanking Against Other US Families by Their Highest Level of Education Achieved ####
 
@@
 
+When looking at @fig-2, we can see that at almost all levels of education, the majority of respondents rank themselves as "average" or lesser.
+This is only false in the group of respondents who have graduate degrees whose majority rank themselves as "above average" or higher.
+Interestingly, we can see that at each level of education, there are respondents who rank themselves as "above average" making it appear that there may be other factors that are relevant in how respondents rank themselves.
+
 ```{r}
@@
 #| warning: false
-#| label: fig-7
-#| fig-cap: "Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved"
+#| label: fig-2
+#| fig-cap: "Respondent's Degree of Job Satisfaction by Their Highest Level of Education Achieved"
 
-#### Creating Graph to Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved ####
+#### Creating Graph to Respondent's Degree of Job Satisfaction by Their Highest Level of Education Achieved ####
 
@@
 
+From looking at @fig-3,
+
+According to **Figure 3**, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
+
 ```{r}
@@
 #| warning: false
-#| label: fig-15
+#| label: fig-3
 #| fig-cap: "Respondent's Report of Financial Satisfaction by Their Highest Level of Education Achieved"
@@
 cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = satfin, fill = degree)) +
+  ggplot(mapping = aes(y = degree, fill = satfin)) +
   geom_bar() + 
   theme_classic() +
-  labs(y = "Financial Satisfaction",
+  labs(y = "Highest Level of Education Achieved",
        x = "Number of Respondents",
-       fill = "Highest Level of Education Achieved")+
+       fill = "Financial Satisfaction")+
   scale_fill_brewer(palette = "Pastel1") +
@@
 #| warning: false
-#| label: fig-17
-#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families"
+#| label: fig-4
+#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families"
 
-#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families ####
+#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families ####
 
@@
 #| warning: false
-#| label: fig-18
-#| fig-cap: "finrela vs satjob"
+#| label: fig-5
+#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"
 
@@
        fill = "Financial Satisfaction")+
+  scale_fill_brewer(palette = "Pastel1") +
+  theme(legend.title = element_text(size = 8),
+        legend.text= element_text(size=8))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-6
+#| fig-cap: "finrela vs class"
+
+#### Creating Graph to ####
+
+cleaned_gss_2021 |>
+ggplot(mapping = aes(y = finrela, fill = class)) +
+geom_bar() +
+theme_classic() +
+labs(y = "finrela",
+x = "number",
+fill = "class")+
 scale_fill_brewer(palette = "Pastel1") +
@@
 Blader examined the impact of status and social class on subjective well-being (SWB).
-They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB **\[cite page 333\]**.
-Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-As shown in **Figure 15**, we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
+They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB [@citeyublader]Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
+As shown in @fig-6 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
 Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.
@@
 
-## Third discussion point
+## Financial Satisfaction
+
+Financial satisfaction as a result of hard work is the core principle within the American Dream, and as a result, Americans are known for their work culture.
+Researchers have tried to investigate the differences between work culture within Europe as well as within the United States and have narrowed it down to a variety of factors that contribute to the culture as it is today.
+Despite the fact that the economies and societal frameworks of Europe and America are very similar, the approach to work within the United States is very different.
+The number of hours worked per year for the average American was about 17% higher than the hours per year for the average European [@citeeuropevacay].
+For this reason, financial satisfaction and social class are very prevalent within the American definition of well-being.
+Job satisfaction ties very closely this idea in the pursuit of the American Dream.
+
+The second largest group of participants who had completed the survey had completed a bachelor's degree.
+In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem.
+According to **Figure 2**, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
+The majority for both groups claimed to be average or above average.
+There was still a significant number of individuals who had chosen below average, even for the group with the highest level of education.
+
+A similar notion exists when comparing an individuals level of education with their job satisfaction.
+According to **Figure 3**, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
+This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
+According to **Figure 4**, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
 
@@
 One weakness is that our insights rely on data from the General Social Survey (GSS), which is a cross-sectional survey that collects data at a single point in time.
-While it can be useful for exploring relationships between variables and generating hypotheses, it cannot establish causality between variables, has limited ability to assess change over time, and has potential for selection bias if participants are not representative of the population of interest **\[cite article\]**.
-Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one's overall well-being.
+While it can be useful for exploring relationships between variables and generating hypotheses, it cannot establish causality between variables, has limited ability to assess change over time, and has potential for selection bias if participants are not representative of the population of interest [@citestrengthsweaknesses]**.** Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one's overall well-being.
 GSS responses are subject to influence by external factors such as recall bias, in which participants may have left out details when reporting about their subjective experiences.
@@
 
+[Supplementary Survey](https://forms.gle/vUCXy927cDnpx5UL9)
+
 \newpage

### 2023-03-15 scripts/00-simulate_data.R
adjust simulated data

@@ -13,8 +13,6 @@
 
 #### Workspace setup ####
 library(tibble)
-library()
-
 
 #### Simulate data ####
 

### 2023-03-15 scripts/04-test_data.R
adjust tests

@@ -23,7 +23,7 @@ simulated_gss_2021$"highest_year_of_education" |>
   length() == 14
 
 #### Test 2 ####
-simulated_gss_2021$"respondents_sex" |>
+simulated_gss_2021$"self_ascribed_comparison_of_financial_status_against_other_american_families" |>
   class() == "character"
 
 #### Test 3 ####

### 2023-03-15 outputs/paper/paper.qmd
add to results section

@@
 
+```{r}
+#| include: false
+
+#### Ordering Financial Satisfaction####
+
+cleaned_gss_2021$satfin <- 
+  factor(cleaned_gss_2021$satfin, 
+         levels = c("Pretty Well Satisfied", "More or Less Satisfied", "Not Satisfied at All"))
+```
+
 When looking at @fig-1, we can see that the majority of respondents have only completed their high school diploma with the next highest response category being bachelor's degree and the third being graduate degrees.
@@
 
-From looking at @fig-3,
-
-According to **Figure 3**, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
+@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction.
+Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education.
+Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that specific type of degree is influential in how respondents may respond.
 

### 2023-03-15 outputs/paper/paper.qmd
add results
add link to supplementary survey

@@
 
-## Source
+## Source {#sec-second-point}
 
@@
 
-## Sampling
+## Sampling {#sec-third-point}
 
@@
 
-## Key Features
+## Key Features {#sec-fourth-point}
 
@@
 ```
+
+## Bias and ethics {#sec-fifth-point}
 
@@
 In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem.
-According to **Figure 2**, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
+According to @fig-2, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
 The majority for both groups claimed to be average or above average.
@@
 A similar notion exists when comparing an individuals level of education with their job satisfaction.
-According to **Figure 3**, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
+According to @fig-3, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
 This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
-According to **Figure 4**, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
+According to @fig-4, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
 
@@
 
-[Supplementary Survey](https://forms.gle/vUCXy927cDnpx5UL9)
+## Supplementary Survey
+
+Supplementary survey is available: [here](https://forms.gle/vUCXy927cDnpx5UL9)
 

### 2023-03-15 outputs/paper/paper.qmd
remove figure 4 and update figure 6

@@
 
-@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction.
-Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education.
-Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that specific type of degree is influential in how respondents may respond.
-
 ```{r}
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-4
-#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families"
-
-#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "Rating Against Other US Families",
-       x = "Number of Respondents",
-       fill = "Job Satisfaction")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
+@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction.
+Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education.
+Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that specific type of degree is influential in how respondents may respond.
 
@@
 #| label: fig-5
-#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"
+#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"
 
-#### Creating Graph to  ####
+#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction ####
 
@@
 #| label: fig-6
-#| fig-cap: "finrela vs class"
+#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class"
 
-#### Creating Graph to ####
+#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class ####
 
@@
   theme_classic() +
-labs(y = "finrela",
-x = "number",
-fill = "class")+
+  labs(
+    y = "Rating Against Other US Families",
+    x = "Number of Respondents",
+    fill = "Social Class") +
   scale_fill_brewer(palette = "Pastel1") +
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## The American Dream
+## The American Dream {#sec-the-american-dream}
 
@@
 
-## Social Class
+## Social Class {#sec-social-class}
 
@@
 
-## Financial Satisfaction
+## Financial Satisfaction {#sec-financial-satisfaction}
 
@@
 In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem.
-According to @fig-2, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
+According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
 The majority for both groups claimed to be average or above average.
@@
 A similar notion exists when comparing an individuals level of education with their job satisfaction.
-According to @fig-3, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
+According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
 This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
-According to @fig-4, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
+According to @fig-3, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
 
-## Limitations and weaknesses
+## Limitations and weaknesses {#sec-limitations-and-weaknesses}
 
@@
 
-\
+# Further reseach  {#sec-fur-reseach}
 

### 2023-03-15 outputs/paper/paper.qmd
relabel figures

@@
 #| warning: false
-#| label: fig-5
+#| label: fig-4
 #| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"
@@
 #| warning: false
-#| label: fig-6
+#| label: fig-5
 #| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class"
@@
 They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB [@citeyublader]Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-As shown in @fig-6 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
+As shown in @fig-5 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
 Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.

### 2023-03-15 outputs/paper/paper.qmd
update results

@@
 The variables we selected for our analysis can be seen in @tbl-1 and their measurement levels can be seen in @tbl-2.
+Responses were measured using likert scales which measured respondents opinions to the questions being asked.
 
@@
   factor(cleaned_gss_2021$satfin, 
-         levels = c("Pretty Well Satisfied", "More or Less Satisfied", "Not Satisfied at All"))
+         levels = c("Not Satisfied at All","More or Less Satisfied", "Pretty Well Satisfied"))
 ```
@@
 Interestingly, a large portion of respondents with higher levels of education still reported themselves as "average" when comparing themselves to other US families.
+Yet in @fig-1, we can see that at almost all levels of education, the majority of respondents rank themselves as "average" or lesser.
+The only group in which this is false, is in the group of respondents who have graduate degrees.
+In this group the majority rank themselves as "above average" or higher.
 Additionally, the rate at which those with less than a high school diploma and high school diplomas self-report ranking when compared to other US households decreases substantially at every measuring point as ranking increases.
+Importantly, we can see that at each level of education, there are respondents who rank themselves as "above average" making it appear that there may be other factors that are relevant in how respondents rank themselves.
 
@@
 
-When looking at @fig-2, we can see that at almost all levels of education, the majority of respondents rank themselves as "average" or lesser.
-This is only false in the group of respondents who have graduate degrees whose majority rank themselves as "above average" or higher.
-Interestingly, we can see that at each level of education, there are respondents who rank themselves as "above average" making it appear that there may be other factors that are relevant in how respondents rank themselves.
+@fig-2 demonstrates that all respondents are likely to rank themselves as "moderately satisfied" or higher in job satisfaction regardless of level of education.
+Interestingly we can see that there is a level of dissatisfaction at from each.
+group of respondents alluding to the idea that education level may not guarantee job satisfaction.
+This is especially clear when comparing those with bachelor's degrees to those with high school diplomas as each have similar levels of satisfaction and dissatisfaction.
 
@@
 
+@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction.
+Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education.
+Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that a specific type of degree is influential in how respondents may respond.
+
 ```{r}
@@
 
-@fig-3 demonstrates that most respondents are "more or less satisfied" or higher when discussing their degree of financial satisfaction.
-Importantly, we can see that those with higher levels of education have higher rates within their group of being "pretty well satisfied" with their financial standing, than those with lower levels of education.
-Additionally, we can see that those with associate or junior college level education are the most balanced in all levels of financial satisfaction, alluding to the idea that specific type of degree is influential in how respondents may respond.
+By looking at @fig-4 we can see that most respondents are "moderately satisfied" or higher with their current employment. Although each has
 
@@
 #| label: fig-4
-#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"
+#| fig-cap: "Respondent's Highest Level of Education Achieved by Job Satisfaction"
 
-#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction ####
+#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Highest Level of Education Achieved ####
 
 cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = satfin)) +
+  ggplot(mapping = aes(y = degree, fill = satjob)) +
   geom_bar() + 
   theme_classic() +
-  labs(y = "Rating Against Other US Families",
+  labs(y = "Highest Level of Education Achieved",
        x = "Number of Respondents",
-       fill = "Financial Satisfaction")+
+       fill = "Job Satisfaction")+
   scale_fill_brewer(palette = "Pastel1") +

### 2023-03-15 scripts/00-simulate_data.R
update and move new simulated data

@@ -20,26 +20,6 @@ set.seed(853)
 
 simulated_gss_2021 <-
   tibble(
-    "highest_year_of_education" = sample(
-      x = c(
-        "7th Grade",
-        "8th Grade",
-        "9th Grade",
-        "10th Grade",
-        "11th Grade",
-        "12th Grade",
-        "1 Year of College",
-        "2 Years of College",
-        "3 Years of College",
-        "4 Years of College",
-        "5 Years of College",
-        "6 Years of College",
-        "7 Years of College",
-        "8 Years of College"
-      ),
-      size = 4032,
-      replace = TRUE
-    ),
     "highest_level_of_education" = sample(
       x = c(
         "Less Than High School",
@@ -51,28 +31,12 @@ simulated_gss_2021 <-
       size = 4032,
       replace = TRUE
     ),
-    "respondents_sex" = sample(
-      x = c(
-        "Male",
-        "Female"
-      ),
-      size = 4032,
-      replace = TRUE
-    ),
     "job_satisfaction" = sample(
       x = c(
         "Very Satisfied",
         "Moderately Satisfied",
         "A Little Dissatisfied",
         "Very Dissatisfied"
-      ),
-      size = 4032,
-      replace = TRUE
-    ),
-    "impact_of_winning_money_on_maintaining_employment" = sample(
-      x = c(
-        "Continue to Work",
-        "Stop Working"
       ),
       size = 4032,
       replace = TRUE
@@ -96,7 +60,7 @@ simulated_gss_2021 <-
       size = 4032,
       replace = TRUE
     ),
-    "self_ascribed_comparison_of_financial_status_against_other_american_families" = sample(
+    "compare_financial_status_against_other_us_families" = sample(
       x = c(
         "Far Below Average",
         "Below Average",

### 2023-03-15 scripts/04-test_data.R
update tests

@@ -18,12 +18,12 @@ simulated_gss_2021 <- read.csv(here::here("./inputs/data/2021_simulated_data/sim
 #### Testing Simulated Data ####
 
 #### Test 1 ####
-simulated_gss_2021$"highest_year_of_education" |>
+simulated_gss_2021$"highest_level_of_education" |>
   unique()|>
-  length() == 14
+  length() == 5
 
 #### Test 2 ####
-simulated_gss_2021$"self_ascribed_comparison_of_financial_status_against_other_american_families" |>
+simulated_gss_2021$"compare_financial_status_against_other_us_families" |>
   class() == "character"
 
 #### Test 3 ####

### 2023-03-15 outputs/paper/paper.qmd
update results

@@
 #| label: fig-4
-#| fig-cap: "Respondent's Highest Level of Education Achieved by Job Satisfaction"
-
-#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Highest Level of Education Achieved ####
-
-cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = degree, fill = satjob)) +
-  geom_bar() + 
-  theme_classic() +
-  labs(y = "Highest Level of Education Achieved",
-       x = "Number of Respondents",
-       fill = "Job Satisfaction")+
-  scale_fill_brewer(palette = "Pastel1") +
-  theme(legend.title = element_text(size = 8),
-        legend.text= element_text(size=8))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-5
 #| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class"
@@
 They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB [@citeyublader]Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-As shown in @fig-5 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
+As shown in @fig-4 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
 Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.

### 2023-03-16 outputs/paper/paper.qmd
update references and future research section

@@
 
-By looking at @fig-4 we can see that most respondents are "moderately satisfied" or higher with their current employment. Although each has
+By looking at @fig-4 we can see that those who rank themselves as "above average" or higher in comparison to other US families, are also more likely to describe themselves as "upper class" than those who rank themselves lower.
+This indicates that respondents are likely self aware of there financial status as it relates to social class.
+This is emphasized in @fig-4, as the opposite is also true with respondents who rate themselves as "below average" or lower, being more likely to describe themselves as "lower class." Interestingly, respondents who rank themselves as average in comparison to other US families tended to rank themselves as "working class" or "middle class" with only 12 respondents claiming to be of "lower class" and 1 respondent claiming to be of "upper class" from this grouping.
 
@@
 
-According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement**(citation).** These are the fundamentals in terms of how Americans generally define their well-being in society.
+According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement [@citerankhirschl]**.** These are the fundamentals in terms of how Americans generally define their well-being in society.
 However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
@@
 In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem.
-According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
+According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor's degree, the reported financial ranking against other families was proportionately very similar for both groups.
 The majority for both groups claimed to be average or above average.
@@
 A similar notion exists when comparing an individuals level of education with their job satisfaction.
-According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\".
+According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor's or graduate degree still consists of those that chose "Moderately Satisfied", "A Little Dissatisfied", and "Very Dissatisfied".
 This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
-According to @fig-3, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.
+According to @fig-3, the two highest levels of education still make up a significant portion of the "More or Less Satisfied" and the "Not Satisfied at All'' groups.
 
@@
 
-# Further reseach  {#sec-fur-reseach}
+# Future Research {#sec-fur-reseach}
+
+More research into this topic is important as it helps us gain a more substantial understanding of American ideals and how certain indicators may influence the rate at which individuals are achieving them, or not achieving them.
+Further research into this topic should explore more specific questions about attitudes towards work, type of work, income, and comparing respondent situations to close acquaintances to better understand American perspectives.
+We have provided a supplementary survey in @sec-appendix that would further build on the US GSS data in relation to our topic.
+Additionally, future research should be conducted over a period of time using the same survey and methodology to better obtain information that is verifiable and encompasses a larger population of the United States.
 
@@
 
-# Appendix
+# Appendix {#sec-appendix}
 
@@
 
-Supplementary survey is available: [here](https://forms.gle/vUCXy927cDnpx5UL9)
+The supplementary survey is available: [here](https://forms.gle/vUCXy927cDnpx5UL9)
+
+```{r, out.width = "500px"}
+#| echo = FALSE
+
+#### Import .png Files of Supplementary Survey ####
+
+knitr::include_graphics("./supplementary_survey/suppl_surv_01.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_2.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_3.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_4.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_5.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_6.png")
+
+```
 

### 2023-03-16 outputs/paper/paper.qmd
replace figure 4

@@
 #| label: fig-4
-#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class"
+#| fig-cap: "Respondent's Self-Ascribed Social Class by Their Highest Level of Education Achieved"
 
@@
 cleaned_gss_2021 |>
-  ggplot(mapping = aes(y = finrela, fill = class)) +
+  ggplot(mapping = aes(y = degree, fill = class)) +
   geom_bar() +
@@
   labs(
-    y = "Rating Against Other US Families",
+    y = "Highest Level of Education Achieved",
     x = "Number of Respondents",

### 2023-03-16 outputs/paper/paper.qmd
update results

@@
 
-By looking at @fig-4 we can see that those who rank themselves as "above average" or higher in comparison to other US families, are also more likely to describe themselves as "upper class" than those who rank themselves lower.
-This indicates that respondents are likely self aware of there financial status as it relates to social class.
-This is emphasized in @fig-4, as the opposite is also true with respondents who rate themselves as "below average" or lower, being more likely to describe themselves as "lower class." Interestingly, respondents who rank themselves as average in comparison to other US families tended to rank themselves as "working class" or "middle class" with only 12 respondents claiming to be of "lower class" and 1 respondent claiming to be of "upper class" from this grouping.
-
 ```{r}

### 2023-03-16 outputs/paper/paper.qmd
update paper

@@
 
+By looking at @fig-4 we can see that those with graduate and bachelor's degrees are much more likely to describe themselves as "upper class" than "lower class." Interestingly, in all levels of education, most respondents ranked themselves as either "working class" or "middle class" this could be influenced by American idealism of "hard-work" or how respondent's see themselves among their peers which is also subjective.
+Additionally, only a very small number of those with associate or junior college degrees and lower education levels describe themselves as "upper class," ranging from 0 to 10% of respondents from these groups.
+
 ```{r}
@@
 Well-being of individuals within the United States therefore, is tracked and monitored through a variety of different factors.
-The aim of this investigation was to determine whether higher educational achievement influenced an individuals perceptions of social class, degree of financial satisfaction and job satisfaction.
+The aim of this investigation is to determine whether higher educational achievement influences respondent\'s perceptions of their social class, degree of financial satisfaction and job satisfaction.
 These factors were chosen because of their significance with regards to the American Dream, a concept that is built off a linear pattern of behavior in terms of economic security.
@@
 
-According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement [@citerankhirschl]**.** These are the fundamentals in terms of how Americans generally define their well-being in society.
-However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
+According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement [@citerankhirschl]**.**These are the fundamentals in terms of how Americans generally define their well-being in society.
+However, no matter how linear an American\'s personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
 But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.
 
-The assumption in general is a higher degree of education translates so an overall greater quality of life or well-being, greater job satisfaction, higher social class, etc.
+The assumption in general is a higher degree of education translates to an overall greater quality of life or well-being, greater job satisfaction, higher social class, etc.
 However, we found that this was not necessarily the case.
-Overall out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor's degree.
-The level of education was compared to a few variables: overall happiness, self-ascribed social class, job satisfaction, and financial ranking against other families in the US.
+Overall, out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor\'s degree.
+The level of education was compared to a few variables: self-ascribed social class, financial satisfaction,  job satisfaction, and financial ranking against other families in the US.
 
@@
 
-Researchers have investigated the correlation between education and happiness, with several studies indicating that a higher level of education is positively associated with greater levels of happiness.
-This relationship may be explained by the fact that education can impact one's self-ascribed social class, which in turn can influence their notion of happiness.
-Higher education can provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility, leading to a higher sense of social status.
-As a result, these individuals may experience greater life satisfaction, which contributes to their overall sense of happiness and security.
+However, in some cases, the positive correlation between higher education and overall subjective well-being is more prominent - resulting in significant tension in our data of consideration.
+Researchers have investigated the relationship between education and one\'s subjective well-being, with several studies indicating that a higher level of education may be positively associated with greater levels of happiness.
+This relationship may be explained by the fact that education can impact one\'s self-ascribed social class, which in turn can influence their notion of happiness.
+Higher education is assumed to provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility - placing people on the path towards a successful American Dream and resulting in a higher sense of one\'s social status.
+As a result, these individuals might experience greater life satisfaction, which contributes to their overall sense of happiness and security.
 
@@
 Blader examined the impact of status and social class on subjective well-being (SWB).
-They found that social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB [@citeyublader]Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-As shown in @fig-4 we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
-Both the research and data point to the link between higher social class and greater levels of self-ascribed satisfaction and happiness.
+They found that often times social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and they proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB **[@citeyublader].** Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
+This insight is evident in @fig-3, where we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting \"Pretty Well Satisfied\" and \"More or Less Satisfied\" than those selecting \"Not Satisfied at All\".
+Out of the 426 responses indicating a \"Pretty Well\" financial satisfaction, 69% of responses were individuals holding Bachelor and Graduate degrees while only 31% held Associate/Junior college, highschool, and less than highschool levels of education.
+In comparison, those who only completed up until the high school level of education have the most responses of \"Not Satisfied at All\".
+70% out of the 390 \"Not Satisfied At All\" responses were individuals who completed highschool education or lower, while only 30% of those holding Bachelor and Graduate degrees indicated a low financial satisfaction.
 
-Overall, there seems to be a significant relationship between education, social class, and one's perceived well-being.
-Education can serve as a key factor in determining an individual's social class as it unlocks opportunities for resources and mobility, which in turn can impact their sense of status and overall sense of happiness.
-At the same time, while higher levels of education may be generally associated with greater levels of happiness, this relationship may not always be a cause and effect correlation.
+In addition, when looking at @fig-4, we found that there are more individuals holding Bachelor and Graduate degrees who have identified themselves as Upper and Middle class in proportion to those with lower levels of education.
+89% of those who selected \"Upper Class\" and 68% of \"Middle Class\" held Bachelor and Graduate degrees.
+Among the 676 responses for \"Working Class\", 471 of those held high school level of education and lower, making up 70% of the responses.
+In sum, we found that both the research and data point to a link between higher social class and greater perceived levels of life satisfaction.
+
+Overall, there seems to be a significant relationship between the data in education, social class, and one\'s perceived well-being.
+Education may serve as an important factor in determining an individual\'s social class as it can unlock opportunities for resources and mobility, which in turn can positively impact their sense of status and overall happiness.
+At the same time, while higher levels of education may be generally associated with greater levels of overall well-being, this relationship may not always be a cause and effect correlation.
 Subjective well-being may be further influenced by other factors such as personal values, cultural background, and social support.
-It is important to consider these important nuances when examining the data in order to develop a more comprehensive understanding of how variables interact and impact individuals' lives.
+It is important to consider these important nuances when examining the data and making assumptions in order to develop a more comprehensive understanding of how variables interact and impact individuals\' lives.
 This will be further explored in the weaknesses, ethics, and bias section of this paper.
@@
 Despite the fact that the economies and societal frameworks of Europe and America are very similar, the approach to work within the United States is very different.
-The number of hours worked per year for the average American was about 17% higher than the hours per year for the average European [@citeeuropevacay].
-For this reason, financial satisfaction and social class are very prevalent within the American definition of well-being.
+The number of hours worked per year for the average American was about 17% higher than the hours per year for the average European.
+[@citeeuropevacay] For this reason, financial satisfaction and social class are very prevalent within the American definition of well-being.
 Job satisfaction ties very closely this idea in the pursuit of the American Dream.
@@
 In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem.
-According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor's degree, the reported financial ranking against other families was proportionately very similar for both groups.
+According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups.
 The majority for both groups claimed to be average or above average.
@@
 A similar notion exists when comparing an individuals level of education with their job satisfaction.
-According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor's or graduate degree still consists of those that chose "Moderately Satisfied", "A Little Dissatisfied", and "Very Dissatisfied".
-This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
-According to @fig-3, the two highest levels of education still make up a significant portion of the "More or Less Satisfied" and the "Not Satisfied at All'' groups.
+According to @fig-2,as the education level rises so does the number of people who are proportionately more satisfied with their jobs.
+However, job satisfaction is fleeting, it is simply a reflection of the current state, and not an overall indication of cumulative job satisfaction.
+According to Figure 3, financial satisfaction rises with an increased level of education, but the group that claims dissatisfaction is a significant number in the bachelor\'s and graduate degree groups.
+It remains a minority, but it is significant nonetheless.
+This points towards the un-attainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction.
 
@@
 One weakness is that our insights rely on data from the General Social Survey (GSS), which is a cross-sectional survey that collects data at a single point in time.
-While it can be useful for exploring relationships between variables and generating hypotheses, it cannot establish causality between variables, has limited ability to assess change over time, and has potential for selection bias if participants are not representative of the population of interest [@citestrengthsweaknesses]**.** Due to the nature of the data being self-reported responses, it may not fully capture the dynamic nature of the ways in which various levels of education affect one's overall well-being.
-GSS responses are subject to influence by external factors such as recall bias, in which participants may have left out details when reporting about their subjective experiences.
+Although it can be helpful in investigating associations between variables and developing hypotheses, the GSS is not capable of establishing causation between variables and has potential for selection bias if participants are not representative of the population of interest [@citestrengthsweaknesses].
+In addition, due to changes in the questions asked over time, the GSS has limited capacity to make exact comparisons - as in the data analyzed in our study, which was collected during a period when the survey was conducted entirely online, which necessitated modifications to the question format in order to accommodate the new platform.
+Above all, due to the nature of the data being self-reported responses, it may not fully capture the dynamic and complicated nature of the ways in which various levels of education affect one\'s overall well-being.
+The General Social Survey responses are subject to influence by a myriad of external factors including recall bias, in which participants may have left out important details when reporting about their subjective experiences.
 
-Another potential ethical concern is that our paper may perpetuate the notion that higher education is the only solution to achieving happiness and success, disregarding the presence of systemic inequalities such as racism and economic inequality that can limit access to education and social mobility.
+Another potential ethical concern is that our paper may inadvertently reinforce the concept of the American Dream, which suggests that higher education is a key factor to achieving happiness and success in life.
+This concern is particularly relevant in @sec-social-class, where we analyze the data as-is without taking into account the presence of systemic inequalities such as racism and economic inequality that can significantly limit access to one\'s education and social mobility.
 Moreover, the sample survey in the GSS may not fully represent the experiences of more marginalized groups, which point to the need for further research and survey strategies that incorporate more diverse perspectives.
 
-In sum, while the paper provides valuable insights on the relationship between education and self-perceived happiness, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our findings.
+In sum, while our paper provides valuable insights on the relationship between education and one\'s perceived well-being, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our insights and findings.
 
@@
 We have provided a supplementary survey in @sec-appendix that would further build on the US GSS data in relation to our topic.
-Additionally, future research should be conducted over a period of time using the same survey and methodology to better obtain information that is verifiable and encompasses a larger population of the United States.
+Additionally, future research should be conducted over a period of time using the same survey and methodology to collect obtain information that is verifiable and encompasses a larger population of the United States.
 

### 2023-03-16 outputs/paper/paper.qmd
update paper
update bias and ethics section

@@
 ## Bias and ethics {#sec-fifth-point}
+
+It is important to note that observations from the 2021 GSS may be influenced by social trends due to the world around them, such as the COVID-19 pandemic along with methodological shifts that occurred for this survey.
+As the GSS changed to a full web-based survey in this year, answers could have been impacted.
+This is why we have chosen not to compare previous survey results.
+Additionally, as this survey was completed online, there is a higher rate of non-response.
+To control for this the 2021 GSS adjusted population totals to ensure that the weighted totals were able to match closely to the U.S Census Bureau estimates by sex, age, education, race, ethnicity, and  region of the country **\[citegsscodebook\]**.
+Additionally due to the online nature of the survey in 2021, household enumeration was not possible and so households had to identify the adult with the most birthday **\[citegsscodebook\]**.
+This could have resulted in respondent selections occurring at the household level or missing some household residents such as people living abroad, adult children, etc.
+**\[citegsscodebook\]**.
+More bias can occur from sampling error in which the sample conducted from this survey could not be representative of the US population **\[citegsscodebook\]**.
+Although, the US GSS does control for this by conducting tests of significance to look for trend differences estimates **\[citegsscodebook\].**
 
@@
 A similar notion exists when comparing an individuals level of education with their job satisfaction.
-According to @fig-2,as the education level rises so does the number of people who are proportionately more satisfied with their jobs.
+According to @fig-2, as the education level rises so does the number of people who are proportionately more satisfied with their jobs.
 However, job satisfaction is fleeting, it is simply a reflection of the current state, and not an overall indication of cumulative job satisfaction.

### 2023-03-16 outputs/paper/paper.qmd
add introduction and update references

@@
 
-# Data and methods {#sec-data}
+In the United States, the concept of the American Dream has been deeply ingrained in the national consciousness for decades.
+It is the idea that through hard work and determination, anyone can achieve success and upward mobility regardless of their background and other significant, uncontrollable factors.
+Within this notion, education is often perceived as one of the key factors in achieving the American Dream, with many individuals in the United States believing that a degree is necessary for financial stability and social status.
+But does this belief reflect reality?
+We analyzed data from the 2021 United States General Social Survey to examine the relationships between education level, self-perceived social class, financial satisfaction, and job satisfaction and how they relate to an individual\'s overall sense of well-being.
+
+We will first discuss the source of our data, its biases, and review the sampling and key features including our estimand of 1,567 responses of the 3,731 complete responses received from male and female US citizens, not living in institutional housing, and who are over the age of 18.
+Then, we will discuss our results through the lens of the American Dream, Social Class, and Financial Satisfaction.  Our findings were surprisingly complex and multifaceted, revealing that the relationships between these variables are not as straightforward as one might think.
+
+A key insight that we found was that despite higher education (Bachelor and Graduate degrees) being positively associated with both financial satisfaction and self-perceived social class in the GSS data, the majority of respondents across all education levels still identified themselves as "working class" or "middle class\", suggesting an influence of the American idealism of \"hard work\".
+Moreover, our results indicated that job satisfaction levels varied significantly among respondents, regardless of their level of education -- indicating that higher education doesn't necessarily guarantee job satisfaction.
+Such findings raise significant tension between the ideal of the American Dream and its relationship to education.
+Our results suggest that the idea that a degree in higher education can put individuals towards a linear path to success and upward mobility is flawed.
+
+Finally, we will take a look at the limitations and weaknesses of our findings in this paper and review the next steps on this particular topic.
+All in all, by examining the GSS survey data, we can shed light on the larger societal implications of the so-called American Dream, question existing assumptions and beliefs, and provide an insightful contribution to the ongoing discourse surrounding education and success in the United States.
+
+# Data and Methods {#sec-data}
 
@@
 
-This paper utilzes the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidyverse], here [@citehere], janitor [@citejanitor],and dplyr [@citedplyr].
+This paper utilizes the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidyverse], here [@citehere], janitor [@citejanitor],and dplyr [@citedplyr].
 All figures in this paper have been created using the packages ggplot2 [@citeggplot2] and the tables have been created using knitr [@citeknitr] and kableExtra [@citekablextra].
@@
 All data within this paper are extracted from the 2021 United States General Social Survey (GSS).
-This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends **\[citegsscodebook\].** Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires **\[citegsscodebook\]**.
-The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures **\[citegsscodebook\].**
+This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends [@citegsscodebook**].** Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires **[@citegsscodebook**].
+The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures [@citegsscodebook]**.**
 
@@
 
-The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing **\[citegsscodebook\].** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses **\[citegsscodebook\]**.
-From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 total surveys released **\[citegsscodebook\].**
+The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing [@citegsscodebook]**.** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses [@citegsscodebook].
+From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch [@citegsscodebook]**.** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 total surveys released [@citegsscodebook]**.**
 
@@
 This paper is assessing our estimand of 1,567 responses of the 3,731 complete responses received which represents 42% of the complete respondents and only 5.7% of the total surveys released.
-Respondent's to the 2021 GSS are males or female US citizens, not living in institutional housing, who are over the age of 18 **\[citegsscodebook\]**.
+Respondent's to the 2021 GSS are males or female US citizens, not living in institutional housing, who are over the age of 18 [@citegsscodebook].
 In our analysis we removed 2,164 responses to account for unanswered or not applicable responses.
@@
 
-## Bias and ethics {#sec-fifth-point}
+## Bias and Ethics {#sec-fifth-point}
 
@@
 Additionally, as this survey was completed online, there is a higher rate of non-response.
-To control for this the 2021 GSS adjusted population totals to ensure that the weighted totals were able to match closely to the U.S Census Bureau estimates by sex, age, education, race, ethnicity, and  region of the country **\[citegsscodebook\]**.
-Additionally due to the online nature of the survey in 2021, household enumeration was not possible and so households had to identify the adult with the most birthday **\[citegsscodebook\]**.
+To control for this the 2021 GSS adjusted population totals to ensure that the weighted totals were able to match closely to the U.S Census Bureau estimates by sex, age, education, race, ethnicity, and  region of the country [@citegsscodebook].
+Additionally due to the online nature of the survey in 2021, household enumeration was not possible and so households had to identify the adult with the most birthday [@citegsscodebook].
 This could have resulted in respondent selections occurring at the household level or missing some household residents such as people living abroad, adult children, etc.
-**\[citegsscodebook\]**.
-More bias can occur from sampling error in which the sample conducted from this survey could not be representative of the US population **\[citegsscodebook\]**.
-Although, the US GSS does control for this by conducting tests of significance to look for trend differences estimates **\[citegsscodebook\].**
+[@citegsscodebook].
+More bias can occur from sampling error in which the sample conducted from this survey could not be representative of the US population [@citegsscodebook].
+Although, the US GSS does control for this by conducting tests of significance to look for trend differences estimates [@citegsscodebook]**.**
 
@@
 
+\newpage
+
 # Discussion {#sec-discussion}
@@
 Well-being of individuals within the United States therefore, is tracked and monitored through a variety of different factors.
-The aim of this investigation is to determine whether higher educational achievement influences respondent\'s perceptions of their social class, degree of financial satisfaction and job satisfaction.
+The aim of this investigation is to determine whether higher educational achievement influences respondent's perceptions of their social class, degree of financial satisfaction and job satisfaction.
 These factors were chosen because of their significance with regards to the American Dream, a concept that is built off a linear pattern of behavior in terms of economic security.
@@
 According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement [@citerankhirschl]**.**These are the fundamentals in terms of how Americans generally define their well-being in society.
-However, no matter how linear an American\'s personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
+However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer.
 But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.
@@
 However, we found that this was not necessarily the case.
-Overall, out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor\'s degree.
+Overall, out of our participants that completed the survey, the largest group had only completed high school, and the second largest group had completed a bachelor's degree.
 The level of education was compared to a few variables: self-ascribed social class, financial satisfaction,  job satisfaction, and financial ranking against other families in the US.
@@
 However, in some cases, the positive correlation between higher education and overall subjective well-being is more prominent - resulting in significant tension in our data of consideration.
-Researchers have investigated the relationship between education and one\'s subjective well-being, with several studies indicating that a higher level of education may be positively associated with greater levels of happiness.
-This relationship may be explained by the fact that education can impact one\'s self-ascribed social class, which in turn can influence their notion of happiness.
-Higher education is assumed to provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility - placing people on the path towards a successful American Dream and resulting in a higher sense of one\'s social status.
+Researchers have investigated the relationship between education and one's subjective well-being, with several studies indicating that a higher level of education may be positively associated with greater levels of happiness.
+This relationship may be explained by the fact that education can impact one's self-ascribed social class, which in turn can influence their notion of happiness.
+Higher education is assumed to provide individuals with better job opportunities, higher income, better access to resources, and greater social mobility - placing people on the path towards a successful American Dream and resulting in a higher sense of one's social status.
 As a result, these individuals might experience greater life satisfaction, which contributes to their overall sense of happiness and security.
@@
 Blader examined the impact of status and social class on subjective well-being (SWB).
-They found that often times social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and they proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB **[@citeyublader].** Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
-This insight is evident in @fig-3, where we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting \"Pretty Well Satisfied\" and \"More or Less Satisfied\" than those selecting \"Not Satisfied at All\".
-Out of the 426 responses indicating a \"Pretty Well\" financial satisfaction, 69% of responses were individuals holding Bachelor and Graduate degrees while only 31% held Associate/Junior college, highschool, and less than highschool levels of education.
-In comparison, those who only completed up until the high school level of education have the most responses of \"Not Satisfied at All\".
-70% out of the 390 \"Not Satisfied At All\" responses were individuals who completed highschool education or lower, while only 30% of those holding Bachelor and Graduate degrees indicated a low financial satisfaction.
+They found that often times social class addresses fundamental psychological needs, such as autonomy, mastery, respect, and occupational prestige, and they proposed that individuals in higher social classes experience greater levels of status and power, leading to higher SWB [@citeyublader]**.** Conversely, individuals in lower social classes feel lower levels of status and power, resulting in lower levels of SWB.
+This insight is evident in @fig-3, where we found that individuals holding Bachelors and Graduate Degrees are proportionally more satisfied with their financial situation, with the large majority selecting "Pretty Well Satisfied" and "More or Less Satisfied" than those selecting "Not Satisfied at All".
+Out of the 426 responses indicating a "Pretty Well" financial satisfaction, 69% of responses were individuals holding Bachelor and Graduate degrees while only 31% held Associate/Junior college, high school, and less than high school levels of education.
+In comparison, those who only completed up until the high school level of education have the most responses of "Not Satisfied at All".
+70% out of the 390 "Not Satisfied At All" responses were individuals who completed high school education or lower, while only 30% of those holding Bachelor and Graduate degrees indicated a low financial satisfaction.
 
 In addition, when looking at @fig-4, we found that there are more individuals holding Bachelor and Graduate degrees who have identified themselves as Upper and Middle class in proportion to those with lower levels of education.
-89% of those who selected \"Upper Class\" and 68% of \"Middle Class\" held Bachelor and Graduate degrees.
-Among the 676 responses for \"Working Class\", 471 of those held high school level of education and lower, making up 70% of the responses.
+89% of those who selected "Upper Class" and 68% of "Middle Class" held Bachelor and Graduate degrees.
+Among the 676 responses for "Working Class", 471 of those held high school level of education and lower, making up 70% of the responses.
 In sum, we found that both the research and data point to a link between higher social class and greater perceived levels of life satisfaction.
 
-Overall, there seems to be a significant relationship between the data in education, social class, and one\'s perceived well-being.
-Education may serve as an important factor in determining an individual\'s social class as it can unlock opportunities for resources and mobility, which in turn can positively impact their sense of status and overall happiness.
+Overall, there seems to be a significant relationship between the data in education, social class, and one's perceived well-being.
+Education may serve as an important factor in determining an individual's social class as it can unlock opportunities for resources and mobility, which in turn can positively impact their sense of status and overall happiness.
 At the same time, while higher levels of education may be generally associated with greater levels of overall well-being, this relationship may not always be a cause and effect correlation.
 Subjective well-being may be further influenced by other factors such as personal values, cultural background, and social support.
-It is important to consider these important nuances when examining the data and making assumptions in order to develop a more comprehensive understanding of how variables interact and impact individuals\' lives.
+It is important to consider these important nuances when examining the data and making assumptions in order to develop a more comprehensive understanding of how variables interact and impact individuals' lives.
 This will be further explored in the weaknesses, ethics, and bias section of this paper.
@@
 However, job satisfaction is fleeting, it is simply a reflection of the current state, and not an overall indication of cumulative job satisfaction.
-According to Figure 3, financial satisfaction rises with an increased level of education, but the group that claims dissatisfaction is a significant number in the bachelor\'s and graduate degree groups.
+According to Figure 3, financial satisfaction rises with an increased level of education, but the group that claims dissatisfaction is a significant number in the bachelor's and graduate degree groups.
 It remains a minority, but it is significant nonetheless.
@@
 
-## Limitations and weaknesses {#sec-limitations-and-weaknesses}
+## Limitations and Weaknesses {#sec-limitations-and-weaknesses}
 
@@
 In addition, due to changes in the questions asked over time, the GSS has limited capacity to make exact comparisons - as in the data analyzed in our study, which was collected during a period when the survey was conducted entirely online, which necessitated modifications to the question format in order to accommodate the new platform.
-Above all, due to the nature of the data being self-reported responses, it may not fully capture the dynamic and complicated nature of the ways in which various levels of education affect one\'s overall well-being.
+Above all, due to the nature of the data being self-reported responses, it may not fully capture the dynamic and complicated nature of the ways in which various levels of education affect one's overall well-being.
 The General Social Survey responses are subject to influence by a myriad of external factors including recall bias, in which participants may have left out important details when reporting about their subjective experiences.
@@
 Another potential ethical concern is that our paper may inadvertently reinforce the concept of the American Dream, which suggests that higher education is a key factor to achieving happiness and success in life.
-This concern is particularly relevant in @sec-social-class, where we analyze the data as-is without taking into account the presence of systemic inequalities such as racism and economic inequality that can significantly limit access to one\'s education and social mobility.
+This concern is particularly relevant in @sec-social-class, where we analyze the data as-is without taking into account the presence of systemic inequalities such as racism and economic inequality that can significantly limit access to one's education and social mobility.
 Moreover, the sample survey in the GSS may not fully represent the experiences of more marginalized groups, which point to the need for further research and survey strategies that incorporate more diverse perspectives.
 
-In sum, while our paper provides valuable insights on the relationship between education and one\'s perceived well-being, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our insights and findings.
+In sum, while our paper provides valuable insights on the relationship between education and one's perceived well-being, it is important to consider the limitations, ethical concerns, and potential biases in the data and interpretation of our insights and findings.
 

### 2023-03-16 outputs/paper/paper.qmd
fix in-text citation

@@
 All data within this paper are extracted from the 2021 United States General Social Survey (GSS).
-This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends [@citegsscodebook**].** Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires **[@citegsscodebook**].
-The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures [@citegsscodebook]**.**
+This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends [@citegsscodebook].
+Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires [@citegsscodebook].The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures [@citegsscodebook]**.**
 
@@
 
-\newpage
-
 # Discussion {#sec-discussion}

### 2023-03-16 outputs/paper/paper.qmd
update title and abstract

@@
 ---
-title: "GSS Education Analysis (Working Title)"
-subtitle: "GSS Education Analysis (Working Subtitle)"
+title: "Higher Levels of Education in the U.S. May Positively Correlate to Greater Levels of Financial Satisfaction and Social Worth"
+subtitle: "An Analysis of 2021 U.S. General Social Survey Data"
 author: 
@@
 date-format: "D MMMM YYYY"
-abstract: "abstract (work in progress)"
+abstract: "The American Dream suggests that success can be attained through hard work, but the extent to which education is necessary for achieving financial stability and social status remains uncertain.
+This report aims to examine the relationship between education and one’s overall well-being by analyzing data from the 2021 United States General Social Survey.
+More specifically, we investigate the correlation between level of education, self-ascribed social class, and financial satisfaction.
+Our findings reveal that these relationships are varied and complex, indicating that higher education does not necessarily guarantee a linear path to success."
 format: pdf

### 2023-03-16 outputs/paper/paper.qmd
update supplementary survey

@@
 knitr::include_graphics("./supplementary_survey/suppl_surv_01.png")
-knitr::include_graphics("./supplementary_survey/suppl_surv_2.png")
-knitr::include_graphics("./supplementary_survey/suppl_surv_3.png")
-knitr::include_graphics("./supplementary_survey/suppl_surv_4.png")
-knitr::include_graphics("./supplementary_survey/suppl_surv_5.png")
-knitr::include_graphics("./supplementary_survey/suppl_surv_6.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_02.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_03.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_04.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_05.png")
+knitr::include_graphics("./supplementary_survey/suppl_surv_06.png")
 

### 2023-03-16 scripts/00-simulate_data.R
update preamble

@@ -6,10 +6,8 @@
 # License: MIT
 # Pre-requisites: To understand data need to know where to find the 2021 US General Social Survey data
 
-
 #### Need to Install These Packages to Run Script ####
 # install.packages("tibble")
-
 
 #### Workspace setup ####
 library(tibble)
@@ -72,7 +70,6 @@ simulated_gss_2021 <-
       replace = TRUE
     )
   )
-
 
 #### Save Simulated Data ####
 write.csv(

### 2023-03-16 scripts/01-download_data.R

@@ -5,7 +5,6 @@
 # Date: 10 March 2023 
 # License: MIT
 # Prerequisites: Need to be able to access and download 2021 GSS data from https://gss.norc.org/get-the-data/stata
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace Set-up ####

### 2023-03-16 scripts/04-test_data.R
Small changes to tests

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Tests simulated data of the 2021 Us General Social Survey. The real data can be downloaded from https://gss.norc.org/get-the-data/stata
+# Purpose: Test the simulated data of the 2021 US General Social Survey. The real data can be downloaded from https://gss.norc.org/get-the-data/stata
 # Author: Chloe Thierstein, Huda Sahaf, Emily Kim 
 # Contact: chloe.thierstein@utoronto.ca, huda.sahaf@mail.utoronto.ca, emilyuna.kim@mail.utoronto.ca
 # Date: 6 March 2023 
 # License: MIT
 # Pre-requisites: Need to be able to load in simulated data
 
-#### Need to Install These Packages to Run Script ####
+#### Need to install these packages to run script ####
 # install.packages("here")
 
 #### Workspace setup ####

### 2023-03-16 scripts/00-simulate_data.R
use readr function for downloading data
Using readr, you can more easily access your project files which is a workaround to your previous manual moving of files!

@@ -8,9 +8,13 @@
 
 #### Need to Install These Packages to Run Script ####
 # install.packages("tibble")
+# install.packages("readr")
+# install.packages("hear")
 
 #### Workspace setup ####
 library(tibble)
+library(readr)
+library(here)
 
 #### Simulate data ####
 
@@ -72,9 +76,7 @@ simulated_gss_2021 <-
   )
 
 #### Save Simulated Data ####
-write.csv(
-  x = simulated_gss_2021,
-  file = "simulated_gss_2021.csv"
-) #move this .csv to 2021_data folder
+write_csv(simulated_gss_2021, here::here("inputs/data/simulated_gss_2021.csv"))
+) #download to inputs/data
 
 
